---
title: "IMO_Data"
author: "sophie"
date: "2024-04-01"
output:
  html_document: default
  pdf_document: default
---
# An R Markdown file to scrape the data from [IMO official website](https://www.imo-official.org/)
## General Idea

fist we need to get the link to the problems and use some variable date to scrape
the tables and change it to a data frame, then clean each table individually and lastly
parsing them all together and saving the result as a .csv file for later cleaning
and analysis.

```{r}
#Loading the tidyverse
library(rvest)
library(tidyverse)
```

## Scraping the first table

We need to establish a fist table, as a basis for all our clean ones to get parsed into.
and as such we start by using the link and some functions to do so

```{r}
#declaring a url variable
url <- 'https://www.imo-official.org/year_statistics.aspx?year=1985'

#using pipes to load the table into the data frame
read_html(url) %>% html_table() %>% data.frame() -> df

#removing extra rows
df <- df[-c(9:20),]

#adding a name to the first column, since it doesn't have one in the webpage
colnames(df)[1] = "Problem Number"

#adding the year to the table
df <- df %>% mutate(Problem_year = 1985)

#our log super table, establishing log as the table where all the other tables will
#get parsed
log = df
log
```

## Looping through the years

Now all that we have to do is to use a for-loop to repeat the process and append
every table of every year to the log super-table, this can be achieved as follows:

```{r}
#creating a list of years to be scraped 
Dates <- c(1986:2023)

#start of for-loop
for (year in Dates){
  
  #pasting the year as a string to the end of each URL to get the desired webpage
  url <- paste('https://www.imo-official.org/year_statistics.aspx?year=',toString(year),sep ="")
  
  #using the df dummy variable to store the scraped raw data
  url %>% read_html %>% html_table() %>% data.frame() -> df
  
  #removing unwanted rows
  df <- df[-c(9:20),]
  
  #filling the empty column name
  colnames(df)[1] = "Problem Number"
  
  #adding the year as an extra column and to make later cleaning easier
  df <- df %>% mutate(Problem_year = year)
  
  #adding the dummy variable df's table to the log super-table, and preparing to
  #repeat the loop
  log <- bind_rows(log, df)

}
```

## Saving the results as .csv 

Analysis and visualizations on [Tableau](https://public.tableau.com/views/InternationalMathematicalOlympiadDataCategoryandDifficulty/Dashboard1?:language=en-GB&:sid=&:display_count=n&:origin=viz_share_link)

```{r}
write.csv(log, "Name_of_your_file.csv")
```

```{r}
htmltools::includeHTML("rrrr.html")
```

